---
title: "Bus Trrafic in Japan"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: cerulean
date: "`r Sys.Date()`"
runitime: shiny
---

```{r setup, include=FALSE}

library(flexdashboard)
library(tidyverse)
library(leaflet)  
library(crosstalk)  
library(RColorBrewer)
library(readr)
library(ggplot2)
library(DT)
library(curl)

```


```{r data, message=FALSE, echo=FALSE, warning=FALSE}

req <- curl_fetch_memory("https://api.odpt.org/api/v4/odpt:Bus?odpt:operator=odpt.Operator:SeibuBus&acl:consumerKey=c1f315c808022db68eb65b5221764083a2964e2da068ecff8f944c233afe96b7")
#jsonlite::prettify(rawToChar(req$content))
bus.data.json <- jsonlite::fromJSON(jsonlite::prettify(rawToChar(req$content)))

rnum<-nrow(bus.data.json)

bus_dat <- bus.data.json  %>% 
  select(lat=`geo:lat`, lng=`geo:long`) %>% 
  mutate(id=c(1:rnum), race=rep(c("A", "A", "B"), length=rnum),  bus_num=rep(c(1:5), length=rnum) ) %>% 
  drop_na()

sd <- SharedData$new(bus_dat)

pal <- colorFactor(
#  palette = 'Spectral',
  palette = c("blue", "red"),
  domain = bus_dat$race
)

sd %>% 
  leaflet() %>%
  setView(lng = 139.5, lat = 35.8 , zoom = 11) %>% 
  addTiles() %>%
  addCircleMarkers(lng = ~lng, lat = ~lat, weight = 3, color = ~pal(race),
                   stroke = TRUE, fillOpacity = 0.5, 
                   #radius = 10,
                   radius = ~ifelse(race == "A", 6, 10),
                   popup = ~paste0("<h5>", bus_dat$id, "</h5>",
                                   
                                   
                                   "<table style='width:100%'>",
                                   
                                   "<tr>",
                                   "<tr>",
                                   "<th>Number</th>",
                                   "<th>", bus_dat$bus_num, "</th>",
                                   "</tr>"
                                   
                   )) %>%
  addLegend("bottomleft", pal = pal, values = ~race,
            title = "Bus",
#            labFormat = labelFormat(prefix = "$"),
            opacity = 1
  ) -> map


DT::datatable(
  filter = "top",
  head(bus_dat, 3000), 
  options = list(
  columnDefs = list(list(className = 'dt-center', targets = c(2:5))),
  pageLength = 100,
#  lengthMenu = c(100, 250, 500, 1000),
#  initComplete = JS(
#    "function(settings, json) {",
#    "$(this.api().table().header()).css({'background-color': '#FFFFE0', 'color': '#000'});",
#    "}"),
  (searchHighlight = TRUE)
)) -> data_table

```




Overview
===================================== 

Column {data-width=650}
-----------------------------------------------------------------------

### Map

```{r map}
map
```

Column {data-width=350}
-----------------------------------------------------------------------

### Filters

```{r filters}

filter_select(
  id = "Race",
  label = "Race",
  sharedData = sd,
  group = ~race
)



```

Data
===================================== 

### Data table

```{r}
data_table
```

Column {data-width=500}
-----------------------------------------------------------------------

###Bus data scraped with curl

Data was scraped with curl command run by R.





Information {data-orientation=rows data-icon="fa-info-circle"}
===================================== 

### Data information

The data used here is taken from 公共交通オープンデータセンター[Public Transportation Open Data Center: Fatal Force](https://www.odpt.org/) website which provides open source data related to transportation in Japan. 
With using dedicated APIs, you can enjoy the data scraping for analysis.

Before you use it, you have to subscribe to take the key  [here](https://developer.odpt.org/users/sign_up).



### Background
Public trasnportation data is useful to learn the data analysis.


### Other information
This dashboard was developed by DiNOV on 24th April 2021.

This dashbaord was developed using [R Studio](https://www.rstudio.com/) and the following packages:

* [RMarkdown](https://rmarkdown.rstudio.com/) for reproducable analysis in quality documents
*  [flexdashbaord](https://rmarkdown.rstudio.com/flexdashboard/) for formatting in RMarkdown
* [DT](https://rstudio.github.io/DT/) for interactive tables
* [crosstalk](https://rstudio.github.io/crosstalk/) for interactive html widgets in RMarkdown


Thanks to Matt Dray for the [excellent guidence](https://github.com/matt-dray/earl18-crosstalk).
```
